\bf\mftitle

### 2011-03-03 doc/jInfer/paper/paper.tex
Documentation: "paper" - review up to line 100.

\section*{Related work}
Most of the algorithms named, doesn't have avalaible implementation, nor are made ready to use.
Probably best solution nowadays is \cite{Bex:2008:SSI:1376616.1376750}.
It deals with schema infering and schema evolution as well.
It employs user interaction, schema visualization and user-aided schema refinement to obtain better results.
Authors use their own algorithms for automatic schema inference (\cite{Bex:2006:ICD:1182635.1164139, Bex:2007:IXS:1325851.1325964}) and then present user generated schema with option of GUI refining it.
Schema refinement and visualization are strong sides of this solution and also possibility to do schema evolution (given old schema and not-all-valid XML documents, update schema) is unique in the field.
Since we both, are trying to solve nearly same problem, we predict that we will approach some good ideas from other solution in further work.
There is no mention of extensibility and pluggable design, however, which we solve as our top priority.

\section*{Short architecture overview}
\begin{figure}
	\centering\includegraphics[width=\myscale\columnwidth]{inference_process}
	\caption{High-level view of the inference process} \label{inference_process}
\end{figure}
We divide the inference process into three steps (as illustrated on fig. \ref{inference_process}):
\begin{enumerate}
	\item Import of various formats (XML/XSD/DTD/XPath) into internal representation - \emph{Initial Grammar}.
	\item Simlification (generalization) of \emph{Initial Grammar} with optional help of user interaction.
	\item Export into various schema formats (XSD/DTD).
\end{enumerate}	
Our internal representation consist of regular grammar, that is list of rules.
We represent right side of grammar rule as regular expression with our own set of classes to represent regular expressions.

On input, all various formats are first converted into internal representation - from XML rules are extracted as positive examples, concatenations, from XSD/DTD rules are extracted as ther are written in schemata. From XPath we extract only explicit concatenations for now.

Rules are send to \jmodule{Simplifier} module, which has to do the simplification algorithm and return \emph{Simplified Grammar}, which is then easily exporter by exporter modules.

\begin{figure}
	\centering\includegraphics[width=\myscale\columnwidth]{screenshot}
	\caption{Visualization of automaton in inference process} \label{screenshot}
\end{figure}
Simplification can be either automatic, or user-aided.
We provide visualization of non-deterministic finite automatons.
This helps algorithms that use merging state algorithm with user interaction.
Using simple API, algorithm developer can call our library to present automaton to user to make human decisions and continue in simplification process.
See figure \ref{screenshot} for automaton visualization tool.

>>>>

\section*{Related work}
Most of the algorithms mentioned don't have an implementation publicly available, nor are they ready to use.
Probably best solution nowadays is \cite{Bex:2008:SSI:1376616.1376750}, dealing with schema inference and evolution.
It employs user interaction, schema visualization and user-aided schema refinement to obtain better results.
Authors use their own algorithms for automatic schema inference (\cite{Bex:2006:ICD:1182635.1164139, Bex:2007:IXS:1325851.1325964}) and then present a user generated schema with optional GUI to refine it.
Schema refinement and visualization are strong points of this solution. Also the possibility to do schema evolution (given old schema and not-all-valid XML documents, update schema) is unique in the field.
Since we both are trying to solve nearly the same problem, we predict that we will approach some good ideas from the other solution in further work.
There is no mention of extensibility or pluggable design, however, which we consider our top priority.

\section*{Short architecture overview}
\begin{figure}
	\centering\includegraphics[width=\myscale\columnwidth]{inference_process}
	\caption{High-level view of the inference process} \label{inference_process}
\end{figure}
We divide the inference process into three steps (as illustrated on fig. \ref{inference_process}):
\begin{enumerate}
	\item Import of various formats (XML/XSD/DTD/XPath/\ldots) into an internal representation - \emph{Initial Grammar}.
	\item Simplification (generalization) of \emph{Initial Grammar} with optional help of user interaction.
	\item Export into various schema formats (XSD/DTD/\ldots).
\end{enumerate}	
Our internal representation is a regular grammar, i.e. a list of rules.
We represent the right side of grammar rule as a regular expression with our own set of classes to represent regexps.

On input, all various formats are at first converted into internal representation - from XML, rules are extracted as positive examples, concatenations; from XSD/DTD, rules are extracted as they are written in the schema. From XPath we extract only explicit concatenations for now.

Rules are sent to \jmodule{Simplifier} module, which has to do the simplification algorithm and return a \emph{Simplified Grammar}, which is then easily exported by \jmodule{Schema Generator} modules.

\begin{figure}
	\centering\includegraphics[width=\myscale\columnwidth]{screenshot}
	\caption{Visualization of automaton in inference process} \label{screenshot}
\end{figure}
Simplification can be either automatic, or user-aided.
We provide visualization of non-deterministic finite automata.
This helps algorithms that use merging state algorithms with user interaction.
Using simple API, algorithm developer can call our library to present the automaton to the user to make human decisions and continue in simplification process.
See figure \ref{screenshot} for an automaton visualization tool.
